### 2015-11-06 CVPR16/Source/abstract.tex
Addressed jasons comments.

\begin{abstract}
This paper studies the problem of segmenting tracked feature points on multiple objects in a video sequence. We consider scenes that contain both dynamic and static objects, which usually appear in the context of autonomous driving (e.g., moving and parked cars), and occlusions among objects. We propose a novel continuous model for modeling objects so that point tracks can be probabilistically and accurately assigned to the corresponding object while accounting for object occlusions. Detailed experiments on the KITTI dataset show the superiority of the proposed method over the baseline method which simply uses detection bounding boxes for resolving occlusions and the state-of-the-art motion segmentation methods which cannot cope well with static objects. As a notable application, we show how our continuous occlusion model benefits the task of 3D localization in autonomous driving.  
\end{abstract}

>>>>

\begin{abstract}
This paper studies the problem of segmenting tracked feature points on multiple objects in a video sequence. We consider scenes that contain both dynamic and static objects, which usually appear in the context of autonomous driving (e.g., moving and parked cars), and occlusions among objects. We propose a novel continuous model for representing objects so that point tracks can be probabilistically and accurately assigned to the corresponding object while accounting for object occlusions. Detailed experiments on the KITTI dataset show the superiority of the proposed method over the baseline method which simply uses detection bounding boxes for resolving occlusions and the state-of-the-art motion segmentation methods which cannot cope well with static objects. We apply our continuous occlusion model to task of 3D localization in autonomous driving and show improvements in results.
\end{abstract}

### 2015-11-06 CVPR16/Source/experiments2.tex
Added more comments about the experiments.
Addressed jasons comments.

In this section, we first benchmark our continuous occlusion model for point-to-object association against the baseline method using detection bounding boxes and state-of-the-art methods for motion segmentation. We then show how the proposed model benefits the task of 3D localization in autonomous driving. For our experiments, we use the KITTI dataset~\cite{geiger2013vision}, which consists of video sequences of road scenes under a variety of driving conditions including highways and residential areas. It also provides ground truth data for different tasks such as segmentation, detection, tracking and 3D localization.

@@

\subsection{Localization Experiment and Results}
We report error in three metrics translation error (t) in meters per car, yaw
error (yaw) in radians per car and dimension error is again meters per car. The
results are shown in Table~\ref{tab:localizationExperiment}.  We compare four
combinations of energies as shown in the table.  The energy $\EnergyTrackNoOcc$
represents the point tracks energy modeled with accounting for occlusion, i.e.,
we remove the term $\Ptransmission$ and model $\EnergyTrack$ in the absence of
$\Ptransmission$. Similarly, $\EnergyBBoxNoOcc$ is the energy without the
modification of $\bSigma$ that accounts for occlusion.  The results show that
use of continuous occlusion model improves the localization accuracy in terms
of all three metrics: translation, yaw and dimension error.

>>>>

In this section, we first benchmark our continuous occlusion model for point-to-object association against a baseline method that uses detection bounding boxes and state-of-the-art methods for motion segmentation. We then show how the proposed model benefits the task of 3D localization in autonomous driving. For our experiments, we use the KITTI dataset~\cite{geiger2013vision}, which consists of video sequences of road scenes under a variety of driving conditions including highways and residential areas. It also provides ground truth data for different tasks such as segmentation, detection, tracking and 3D localization.

@@

\subsection{Localization Experiment and Results}
We report error in three metrics translation error (t) in meters per car, yaw
error (yaw) in radians per car and dimension error is again meters per car. The
results are shown in Table~\ref{tab:localizationExperiment}.  We compare four
combinations of energies as shown in the table.  The energy $\EnergyTrackNoOcc$
represents the point tracks energy modeled with accounting for occlusion, i.e.,
we remove the term $\Ptransmission$ and model $\EnergyTrack$ in the absence of
$\Ptransmission$. Similarly, $\EnergyBBoxNoOcc$ is the energy without the
modification of $\Sigma^{(d)}_j$ that accounts for occlusion.  The results show that
use of continuous occlusion model improves the localization accuracy in terms
of all three metrics: translation, yaw and dimension error.

### 2015-11-06 CVPR16/Source/intro.tex
Addressed jasons comments.

Our main contribution is a novel theoretical model for occlusion handling that is continuous and fully 3D. Our model is motivated by insights from computer graphics, whereby we represent objects as translucent 3D ellipsoids. In Section \ref{sec:setup}, we develop novel continuous models for representing \emph{transmission} and \emph{reflection} probabilities for each ray emanating from the camera. This allows assigning probabilities for each point in space belonging to an object, which can explicitly explain image observations and reason about occlusions. This is in contrast to prior works that consider occlusions in 2D, or through discrete occluder patterns that are not physically interpretable.

>>>>

Our main contribution is a novel theoretical model for occlusion handling that is continuous and fully 3D. Our model is motivated by insights from computer graphics, whereby we represent objects as translucent 3D ellipsoids. In Section \ref{sec:setup}, we develop novel continuous models for representing \emph{transmission} and \emph{reflection} probabilities for each ray emanating from the camera. This allows assigning probabilities for each point in space belonging to an object, which can explicitly explain image observations and reason about occlusions. This is in contrast to prior works that consider occlusions in 2D, either through discrete occluder patterns or models that are not physically interpretable.
